---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

library(tidyverse)

# Importing dataset
logged_data <- read_csv('https://docs.google.com/spreadsheets/d/e/2PACX-1vQ1qpjNoWcstl1u-n4g-HL1JLri9caaAR8sw3YfALqo_88nnLyeO8NjOIMaloFxaY91jbzLZMo5HDho/pub?gid=1670447620&single=true&output=csv', show_col_types = FALSE)

# Renaming each column 
latest_data <- logged_data %>%
  rename('name'='Who is filling out this form (first name)',
         'date'="What's the date and time of occurrence?",
         'duration'='How long approximately, were you distracted (minutes)', 
         'distraction_type'='What were you distracted by?', 
         'location'='Where were you studying?',
         'gave_up'='Did you go back to studying, or did you give up?')

# Final code for dynamic report

# Exploring the data set
average_duration <- mean(latest_data$duration)
maximum_duration <- max(latest_data$duration)
minimum_duration <- min(latest_data$duration)
distraction_counts <- count(latest_data, distraction_type)
most_common_distraction <- latest_data %>%
  count(distraction_type, sort = TRUE) %>%
  slice(1) %>%
  pull(distraction_type)
```

```{css}
pre {
  border: 1px solid #4080a8;
  border-radius: 10px;
  background-color: #e3f1fa;
}

body {
  font-family: "Segoe UI", "Helvetica Neue", sans-serif;
  background-color: #cbe6f7;
  
}

title {
  text: bold;
}

h2 {
  color: #1e90ff;
  font-weight: bold;
}

img {
  border: 1px solid #4080a8;
  border-radius: 10px;
}
```

## Investigating patterns of distractions from my studies

Over the last week I have documented each time I have been distracted from my studies, making note of how long I was distracted, what the distraction was, and where I was studying. The goal of this report is to identify patterns in my study habits and find ways to reduce distractions.

Across all logged distractions, the average distraction lasted approximately `r round(average_duration, 1)` minutes.

The longest distraction lasted `r maximum_duration` minutes, while the shortest distraction lasted `r minimum_duration` minutes.

The most common type of distraction was `r most_common_distraction`.

## Number of distractions by type

```{r}
latest_data %>%
  count(distraction_type) %>%
  ggplot(aes(x = distraction_type, y = n)) +
  geom_col() +
  labs(
    title = 'Number of distractions by type',
    x = 'Type of distraction',
    y = 'Frequency of distractions'
  )
```

This graph shows which types of distractions happened most often during the week.

## Number of distractions by study location

```{r}
latest_data %>%
  count(location) %>%
  ggplot(aes(x = location, y = n)) +
  geom_col() +
  labs(
    title = 'Number of distractions by study location',
    x = 'Study location',
    y = 'Frequency of distractions'
  )
```

This graph shows which study locations were linked to the highest number of distractions.

## Duration of distractions at each study location

```{r}
latest_data %>%
  ggplot(aes(x = location, y = duration)) +
  geom_boxplot() +
  labs(
    title = 'Duration of distractions at each study location',
    x = 'Study location',
    y = 'Duration of distraction (minutes)'
  )
```

This boxplot compares how long distractions lasted depending on where I was studying.